# Data Overview

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(forcats)
library(stringr)
library(ggpubr)
library(GGally)
library(ggcorrplot)
library(psych)
library(grid)
library(gridExtra)
library(plotly)
library(viridis)
library(broom)
library(moderndive)
library(infer)
library(broom.mixed)
library(jtools)
library(modelr)
library(FactoMineR)
library(factoextra)
library(lavaan)
library(pheatmap)
library(RFLPtools)
library(gplots)
library(kableExtra)
options(dplyr.summarise.inform = FALSE)
```

```{r raw_data, include=FALSE, warning=FALSE, message=FALSE}
# Importing Data
data <- read_csv("FaceRecData.csv")
```

```{r processed_data}

data_opinion <- data %>%
  map_df(~as_factor(.))

# Skipping this part as we do not want reverse scoring
# Converting the columns of reverse scored ones to factors(i.e. change the level ordering of them)
# rev_order <- c("SA1")

# for (rev_col in rev_order) {
#    data_opinion[[rev_col]] <- fct_rev(data_opinion[[rev_col]])
# }

data_opinion <- data_opinion %>%
  select(matches("^MEM."), matches("^ATTNPER."), matches("^SOC."), matches("^FAC."))

# Converting personal info to factors
data_personal <- data[,1:2] %>%
  map_df(~factor(.))

# Encoded Data
data_enc <- data %>%
  map_df(~as.numeric(.))

# Scaling the data properly
data_enc_1 <- data_enc
for (i in 1:6) {
  data_enc_1[[i+1]] <- data_enc_1[[i+1]]/6
  data_enc_1[[12+i]] <- data_enc_1[[12+i]]/6
}
data_enc_1[,8:12] <- data_enc_1[,8:12]/5
data_enc_1[,19:ncol(data_enc)] <- data_enc_1[,19:ncol(data_enc)]/7

# Net Score Data for each category
data_net_score <- data_enc %>%
  transmute(
    Sex = Sex,
    MEM = (MEM1+MEM2+MEM3+MEM4+MEM5+MEM6)*100/30,
    ATTNPER = (ATTNPER1+ATTNPER2+ATTNPER3+ATTNPER4+ATTNPER5)*100/25,
    SOC = (SOC1+SOC2+SOC3+SOC4+SOC5+SOC6)*100/30,
    FAC = (FAC1+FAC2+FAC2+FAC3+FAC4+FAC5+FAC6+FAC7)*100/35
  )

# Total Score
data_tot_score <- data_enc %>%
  mutate(Score = (MEM1+MEM2+MEM3+MEM4+MEM5+MEM6+ATTNPER1+ATTNPER2+ATTNPER3+ATTNPER4+ATTNPER5+SOC1+SOC2+SOC3+SOC4+SOC5+SOC6+FAC1+FAC2+FAC2+FAC3+FAC4+FAC5+FAC6+FAC7)*100/120) %>%
  select(Sex, Score)
```

Here we shall explore the data we have collected from the `r nrow(data_enc)` college students of India as a response to a survey form given to them. First we shall look at the survey form, then look at the actual data we have collected and as the last part of this section we shall see the different variables and domains involved in this study.

## Survey Form

To conduct the face recognition study, we circulated a survey form among college students of India through Google Forms. The Survey form comprised of 4 sections, each section pertaining to a particular domain of face recognition ability. Each section comprised of 5-7 questions framed to test the response towards that particular aspect of face recognition ability among students of India. Let's look at the sections and the questions asked in the form itself.

### Domains

**These can also be referred to as the study variables** and we have collected data on the following 4 domains of face recognition ability. These domains comprise of the overall face recognition ability of an individual. The domains are as follow:

-   **Memory(abbv. as MEM)**: It deals with the aspect of how humans remember familiar and unfamiliar faces. It also keeps a record of whether we can track the information about the identity of a person. We also see how well we remember our past friends and people we have met.

-   **Attention & Perception(ATTNPER)**: It deals with how attentive we are to various parts of the face. How human faces are perceived by the society. It also deals with how human brain treat face as an important aspect of information processing.

-   **Social Understanding(SOC)**: It deals with how human face plays an important role in communication and interacting with the society. It also deals with how humans tend to prefer some pre-set standards of beauty in terms of facial look.

-   **Facial Features(FAC)**: It deals with what preferences in terms of external facial features prevails in the society. It also deals with the aspect of how a person looks at external beauty like shape, size, eyes, facial hair, smile, etc of a person's face.

### Questions

Here we will see the actual questions asked in the Survey Questionnaire Form. Each of these items club together to form the study variables, which further club together to form the overall pro-environmental attitude.

-   **REC**

    -   **REC1**: I think recycling of products is important.

    -   **REC2**: I upcycle old products into new and useful items.

    -   **REC3**: I believe recycling reduces the consumption of new raw materials.

    -   **REC4**: I like to learn more about product recycling.

    -   **REC5**: I believe recycling is truly beneficial for the environment.

    -   **REC6**: I believe recycling reduces waste production.

    -   **REC7**: I believe recycling promotes sustainable living.

-   **SA**

    -   **SA1**: Safe disposal of waste products is costly.

    -   **SA2**: I believe there should be a fine imposed on people who don't follow proper protocols.

    -   **SA3**: Strict policies should be put into place to conserve the environment.

    -   **SA4**: I believe proper precaution should be taken when dealing with toxic chemicals.

    -   **SA5**: Precautionary measures should be undertaken in a firm manner with regard to natural disasters.

    -   **SA6**: I feel policies should be put in place to increase environmental safety.

-   **PC**

    -   **PC1**: I feel I am adept at managing waste around my surroundings.

    -   **PC2**: I often feel as though one single person cannot change the environment.

    -   **PC3**: I believe my actions are responsible for climate change.

    -   **PC4**: I think environmental conservation is everyone's responsibility.

    -   **PC5**: I believe our cumulative efforts can reduce global warming.

    -   **PC6**: I believe that I can control environmental pollution.

-   **SS**

    -   **SS1**: I believe that an individual alone cannot help in conserving the environment without social support.

    -   **SS2**: I prefer participating in mass clean-up drives to reduce pollution.

    -   **SS3**: Creating nature clubs can help generate awareness about environmental issues.

    -   **SS4**: I like volunteering my services for habitat management work.

    -   **SS5**: I believe in social support for environment protection through the local clubs and NGOs.

-   **ER**

    -   **ER1**: I believe closing the taps when we brush can help save water.

    -   **ER2**: I feel the Earth has plenty of natural resources if we just learn how to effectively use them.

    -   **ER3**: I firmly support closing the lights and fans in a room before leaving it.

    -   **ER4**: I feel all products (like shampoo and soap) should be used till the very end.

    -   **ER5**: I feel everyone should switch to eco-friendly methods more frequently.

-   **ES**

    -   **ES1**: I like working in well-illuminated, airy places.

    -   **ES2**: Disordered surroundings make me anxious.

    -   **ES3**: Crowded places make me feel uneasy.

    -   **ES4**: Very loud noise or music makes me uncomfortable.

    -   **ES5**: I feel irritated when I see garbage thrown on the road and the roadside.

-   **RES**

    -   **RES1**: I find new ways to use waste products.

    -   **RES2**: Items should be repaired before deciding to throw them away.

    -   **RES3**: I like buying products that can be used again, rather than disposable items.

    -   **RES4**: Reuse preserves natural resources.

    -   **RES5**: I look for new ways to reuse old products.

-   **CON**

    -   **CON1**: Regular awareness programs can help conserve the natural environment.

    -   **CON2**: I try to find ways to conserve natural resources in daily life.

    -   **CON3**: Conservation can help create a greener planet for the future.

    -   **CON4**: I feel social media platforms can be used to promote nature conservation.

    -   **CON5**: I intend to save natural resources whenever possible.

-   **END**

### Response

All the items accepted response in the form of a Likert Scale having 5 levels, which are

-   **Strongly Disagree**(Score: 1)

-   **Disagree**(Score: 2)

-   **Neutral**(Score: 3)

-   **Strongly Agree**(Score: 4)

-   **Agree**(Score: 5)

We also asked the same question in different manner to check the consistency of individual towards pro-environmental attitude.

## Population

The Data is collected from only the college and university students of India, who are in the age range of approximately 18 to 25. We have students participating from various colleges and universities and various majors or areas of study fill this Survey Questionnaire Form. We are hence, targeting to study the pro-environmental behavior of this population using our sample.

## Collection

The data was collected from the `r nrow(data)` college students of India via google forms. The sample is not a random sample and we used a method known as the snowball sampling to gather more students to fill the Survey form. The survey form had sections referring to each domain and data was stored in Google Sheets from where it was obtained as a CSV file to conduct our analysis.

## Data

Here we present the collected data from `r nrow(data)` college students.

```{r display_raw_data}
kable(data, caption = "Collected Response of College Students of India on Pro-Environmental Attitude Questionnaire") %>%
  kable_styling(position = "center") %>%
  scroll_box(width = "100%", height = "500px")
```

Since, we are going to conduct statistical analysis with this data, we proceed with the above data after converting each column to their respected score i.e. numerical in nature and hence makes sense to carry forward with all sorts of statistical tools.

The data collected for the study is available on the github repository for this project([here](https://github.com/RishiDarkDevil/Pro-Environmental-Attitude-Analysis/blob/main/PEAData.csv)).
